Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-16 paper/ms.tex
Adding @sivaramambikasaran as a co-author

\author{%
    Daniel~Foreman-Mackey\altaffilmark{\sagan,\uw},
    Eric~Agol\altaffilmark{\uw}, and
    Ruth~Angus\altaffilmark{\simons,\columbia}
}

>>>>

\edef \iss {\arabic{affilcounter}}\stepcounter{affilcounter}
\altaffiltext{\iss}{Department of Computational and Data Sciences,
                    Indian Institute of Science, Bangalore, India}

\author{%
    Daniel~Foreman-Mackey\altaffilmark{\sagan,\uw},
    Eric~Agol\altaffilmark{\uw},
    Ruth~Angus\altaffilmark{\simons,\columbia}, and
    Sivaram~Ambikasaran\altaffilmark{\iss}
}
